Data Management for LSST Special Programs

### 2024-03-27 sec_proc.tex
JB comments

\textbf{Special Processing timescales --}
The timescales for Special Processing should be adopted that best serve the
primary science goal for the Special Program.
For example, nighly-coadd difference-image analysis for DDFs is the most
scientifically useful if done on a daily cadence, but the deeply coadded
images for DDF fields could be released annually.

@@

In cases like this, a set of unique and separate data products with the same formats as the 
time-domain DIA and static-sky data products described in Section~\ref{sssec:proc_reg_dr}
should be created with Special Processing.
They might be released with an annual data release or on an intermediate timescale, e.g.,
within six months of the conclusion of the mini-survey observations.

>>>>

\textbf{Special Processing timescales --}
The timescales for Special Processing should be adopted that best serve the
primary science goal for the Special Program.
For example, nightly-coadd difference-image analysis for DDFs is the most
scientifically useful if done on a daily cadence, but the deeply coadded
images for DDF fields could be released annually.

@@

In cases like this, a set of unique and separate data products with the same formats as the 
time-domain DIA and static-sky data products described in Section~\ref{sssec:proc_reg_dr}
could be created with Special Processing, if they are necessary 
(i.e., Special Processing and data products will not be made if they will be redundant
with the products of Standard Processing).
They might be released with an annual data release or on an intermediate timescale, e.g.,
within six months of the conclusion of the mini-survey observations.
